%-------------------------
% Resume in Latex
% Author : Ismail Sunni
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{ismailsunni.id}{\Large Ismail Sunni}} \\
  Web: \href{ismailsunni.id}{ismailsunni.id} & Email : \href{mailto:imajimatika@gmail.com}{imajimatika@gmail.com}\\
  Github: \href{https://github.com/ismailsunni}{github.com/ismailsunni} & Mobile : +62 813 2861 7492 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universitat Jaume I; University of Muenster}{Castellon, Spain; Muenster, Germany}
      {Master of Science in Geospatial Technologies}{Sept. 2018 -- March 2020 }
    % \resumeSubheading
    %   {Chonnam National University}{Gwangju, South Korea}
    %   {Electronics and Computer Engineering Integrate's program; unfinished }{Sept. 2013 -- Feb. 2014 }
    \resumeSubheading
      {Institut Teknologi Bandung}{Bandung, Indonesia}
      {Bachelor of Science in Informatic Engineering;  GPA: 3.65/4 }{Aug. 2008 -- July. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Camptocamp Germany GmbH}{Munich, Germany}
      {Software Engineer}{April 2020 - now}
    \resumeSubheading
      {Kartoza}{South Africa}
      {Software Engineer}{Mar 2014 - Aug 2018}
      \resumeItemListStart
        \resumeItem{\href{http://inasafe.org/}{InaSAFE}}
          {InaSAFE is free software that produces realistic natural hazard impact scenarios for better planning, preparedness and response activities. Implemented as QGIS plugin and extended as near-realtime analysis. Tech: Python, PyQGIS, PyQt}
        \resumeItem{GeoNode with QGIS Server}
          {Develop an early version of supporting GeoNode with QGIS Server. Tech: Django, Python, QGIS Server}
        \resumeItem{GeoNode Integration on QGIS}
          {Adding GeoNode support on QGIS. Tech: Qt C++}
        \resumeItem{\href{https://github.com/inasafe/inasafe-realtime}{InaSAFE Realtime}}
          {Implement InaSAFE to do near-real-time disaster analysis. Tech: Python, Django, Docker.}
        \resumeItem{\href{https://github.com/kartoza/geocontext}{GeoContext}}
          {GeoContext is a service that will fetch data for a geographic position. Tech: Python, Django, Django Rest Framework.}
        \resumeItem{\href{http://plugins.qgis.org/plugins/SGDiagramDownloader/}{SG Diagram Downloader}}
          {A QGIS plugin that will download SG (South African Surveyor General) diagrams. Tech: Python, PyQGIS, PyQt.}
        \resumeItem{\href{http://plugins.qgis.org/plugins/StreamFeatureExtractor/}{Stream Feature Extractor}}
          {A QGIS plugin to extract features from a stream network. Tech: Python, PyQGIS, PyQt.}
        \resumeItem{\href{https://github.com/kartoza/prj.app}{Projecta}}
          {A Django app for creating visual changelogs for software releases. Deployed on \href{QGIS Changelog}{http://changelog.qgis.org/}, \href{Kartoza Changelog}{http://changelog.kartoza.com/en/}. Tech: Python, Django}
        \resumeItem{QGIS and InaSAFE Training}
          {Give training for QGIS and InaSAFE in Indonesia and Malawi.}
        \resumeItem{FloodHack 2016}
          {Organizing hackathon for solving flood problem in Jakarta, Indonesia.}
        \resumeItem{Various Web GIS}
          {Develop custom Web GIS based on the customer's requirement. Tech: Python, Django, Leaflet, Docker}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Chonnam National University}{Gwangju, South Korea}
    %   {Research Student}{Sept 2013 - Feb 2014}
    %   \resumeItemListStart
    %     \resumeItem{Wifi Handover Project}
    %       {Research about wifi handover project for android device.}
    %   \resumeItemListEnd

    \resumeSubheading
      {Australia Indonesia Facility For Disaster Reduction}{Jakarta, Indonesia}
      {Software Engineer}{Aug 2012 - July 2013}
      \resumeItemListStart
        \resumeItem{InaSAFE}
          {InaSAFE is free software that produces realistic natural hazard impact scenarios for better planning, preparedness and response activities. Implemented as QGIS plugin. Tech: Python, PyQGIS, PyQt}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://ismailsunni.github.io/GSoC-2019/}{Google Summer of Code 2019 participant with OSGeo.}}
      {QGIS 3D Improvement: On Screen Navigation, Bookmarks, Rendering Point Feature as Billboard, and Measuring Tool. Tech: Qt C++, 3D Programming}
    \resumeSubItem{Docker QGIS 3 Model}
      {Running QGIS 3 Model inside Docker. Tech: Docker, Python, QGIS}
    \resumeSubItem{\href{https://github.com/ismailsunni/f3-factor-finder}{F3: Factor Finder}}
      {Sentiment Analysis and Sentimental Topic Extraction from Opinion about Public Figure Opinion in Bahasa Indonesia. Tech: Python, Sentiment Analysis, NLTK}
    \resumeItem{\href{https://github.com/ismailsunni/altRnative}{altRnative}}
      {R package to run and benchmark R script across R implementation and OS. Tech: R, Docker.}
    \resumeItem{\href{https://github.com/ismailsunni/pedestrian-routing}{Pedestrian Routing}}
      {Implement landmark extraction and routing algorithm based on A* with landmarks for the pedestrian. Tech: Python.}
  \resumeSubHeadingListEnd

%-----------MISCCELLANEOUS-----------------
\section{Misccellaneous}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{http://mastergeotech.info/}{Erasmus Mundus Scholarship}}
      {Scholarship for pursuing master of geospatial technology in Spain, Portugal, and Germany, 2018-2020}
    \resumeSubItem{OSGeo Travel Grant}
      {Travel grant for presenting my Google Summer of Code project with OSGeo at FOSS4G Belgium 2019 Conference}
    \resumeSubItem{\href{http://python.or.id/}{Indonesia Python Community}}
      {Act as treasurer of the community and Python community meet-up organizer in Yogyakarta (inactive), Indonesia: \url{http://python.or.id/}}
    \resumeSubItem{\href{https://qgis-id.github.io}{Indonesia QGIS User Group}}
      {Founder of Indonesia QGIS User Group: \url{https://qgis-id.github.io}}
    % \resumeSubItem{FIFAFU Footbal}
    %   {Organizer of FIFAFU League for a mini Fantasy Premier League: \url{https://twitter.com/FPL_FIFAFU}}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
% \section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Python, Qt C++}
%      \hfill
%      \textbf{Technologies}{: Django, Docker,}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
